Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Large scale definition as part of background

@@

The research process is presented starting from the research questions. After
that we present the definition of large scale which this research builds upon.
The bulk of this section concentrates on presenting the steps of the research
process, starting from the definition of inclusion criteria, continuing with
describing how the primary studies were selected, and finally presenting the
method for analyzing and synthesizing the primary studies. The section concludes
with a discussion on limitations of the method.

>>>>

In this chapter we present existing background literature for this work. This
chapter begins with an overview of agile software development. The second
part presents an overview of existing studies on introducing agile in large
organizations. The last part of this chapter defines large scale in the context
of this study.

@@

The research process is presented starting with the research questions.
%After that we present the definition of large scale which this research builds upon.
The bulk of this section concentrates on presenting the steps of the research
process, starting from the definition of inclusion criteria, continuing with
describing how the primary studies were selected, and finally presenting the
method for analyzing and synthesizing the primary studies.
%The section concludes with a discussion on limitations of the method.
